Accelerating Biomolecular Nuclear Magnetic Resonance Assignment with A*

### 2014-03-26 paper/tex/Paper.tex
paper update

\title{Sample MICS Paper Title}

\author{
Mary Smith and Joe Jones\\
Name of Department\\
Name of Institution\\
City, State Zip\\
Contact email
}
\date{}

@@

\newpage
\setcounter{page}{1}

example cite\cite{Alipanahi09ipass:error}

\section{Method} % (fold)
\label{sec:method}

>>>>

\title{Accelerating Biomolecular Nuclear Magnetic Resonance Assignment with A*}

\author{
Joel Venzke, Paxten Johnson, Rachel Davis, John Emmons, Katherine Roth,\\ David Mascharka, Leah Robison, Timothy Urness and Adina Kilpatrick\\
Department of Mathematics and Computer Science\\
Drake University\\
Des Moines, IA\\
email %TODO
}
\date{}

@@

\setcounter{page}{1}

\section{Introduction}
Several types of NMR variables can be used in the analysis of protein structures. In particular, essential information is provided by the chemical shifts of NMR-active nuclei present in proteins, including hydrogen and isotopes of carbon and nitrogen. The chemical shift is a quantifier for the deviation in the resonant frequency of a nucleus from its value in a structure-free environment, and therefore provides information on the local conformation. Determining the chemical shifts of all or most of the nuclei in a biomolecule is the first step in determining its structure. An important set of chemical shifts in a protein are those corresponding to the nuclei in the backbone of the protein polypeptide chain, including the nitrogen, attached hydrogen, and the alpha and beta carbon atoms ($C_\alpha$ and $C_{\beta}$) of each residue. These chemical shifts are measured using various three-dimensional NMR experiments, and then matched to the individual residues in the protein in a process called sequential assignment.

A prerequisite of the assignment process is data collection using experiments that can provide connectivities between neighboring residues. For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_{\beta}$ nuclei of one residue (residue i), as well as the $C_\alpha$ and $C_{\beta}$ chemical shifts of the immediately preceding residue (residue $i – 1$). In this experiment, the values corresponding to residue i can usually be distinguished from the ($i -1$) values by their higher intensity. However, ambiguities can arise if the intensities are comparable or if the chemical shift values are overlapping. These ambiguities can be resolved by using additional experiments, such as CBCA(CO) NH, which yields the chemical shifts of the preceding residue only. Using all inter-residue connectivities, a chain of correlations through the protein backbone chemical shifts can be established.  This pattern of sequentially linked chemical shift values reflects the sequential linear arrangement of the individual residues in the protein sequence. The pattern is then matched with the protein sequence, by using the fact that certain residues have characteristic $C_\alpha$ and $C_{\beta}$ chemical shift ranges which uniquely identify them. Thus, each measured chemical shift is assigned to a protein residue, and this information can then be used to infer structural information about the biomolecule.
\section{Method} % (fold)
\label{sec:method}
